%-----------------------------------------
% Matthew Medal
% Resumé
%
% URL: http://github.com/mmedal/My-Resume

% Adapted from Michael Wright (mdwrigh2@ncsu.edu)
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[darkred]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}

% Personal Information
\firstname{Matthew}
\familyname{Medal}
\address{5296 Centerhart Ct.}{San Jose, CA 95123}
\mobile{(408) 460-2148}
\email{mmedal@scu.edu}

\title{Matthew Medal's Resume}

\nopagenumbers{}

\begin{document}

\maketitle
\section{Education}
\cventry{2010-2014 (expected)}{Computer Science \& Mathematics, Santa Clara University}{Santa Clara, CA}{}{Total GPA: 3.5}{CSCI \& MA Major GPA: N/A}
\cventry{2006-2010}{Bellarmine College Preparatory}{San Jose, CA}{}{Total GPA: 4.0}{\vspace{1 mm}}
\section{Computer Skills} 
  \cvline{Languages:}{C, C++, Cobol, Fortran, Lisp, MPI, Pascal, Python, Shell}
  \cvline{IDEs:}{Eclipse, QT Creator, Xcode}
  \cvline{Operating Systems:}{OS X, Redhat, Ubuntu, Windows}
  \cvline{Familiarity:}{Active Directory, iOS/Android Development, Linux FileSystem, SNMP, Splunk}
  \cvline{CSCI Courses Taken:}{Intro to C++, Object Oriented Programming, Data Structures, Embedded Systems \& Assembly Language, Logic Design, Comparative Programming Languages, Theory of Automata}
  \cvline{MA Courses Taken:}{Calculus I-IV, Linear Algebra, Discrete Math, Formal Writing/Publishing in Mathematics}
  \cvline{}{}
\section{Experience} 
  \cventry{Summer 2012}{Operations IAAS Intern}{eBay}{San Jose, CA}{}{
    \begin{itemize}
      \item Design and implement suite of python-based SA tools for monitoring and reporting on SAN/NAS storage usage.
      \item Design and implement a complete SNMP monitoring solution for trap management utilizing custom built parse tools, net-snmp, and Splunk.
      \item Maintain a complete understanding of IPMI, SNMP, Django, and Manufacturer-specific hardware differences for LOMs.
    \end{itemize}
  }
  \cventry{2010--2012}{IT Technician}{Bellarmine College Prep}{San Jose, CA}{}{
    \begin{itemize}
      \item Maintain and provide hardware support for computer network on a campus of 1600 students.
      \item Work one-on-one with faculty/staff on technology related issues.
      \item Assist IT Director with tasks as-needed, ranging from racking servers to rewiring network switches to creating an OSX re-imaging solution.
    \end{itemize}
  }
  \cventry{May 2007--\\August 2009}{Tennis Instructor}{SJ Swim \& Racquet Club}{San Jose, CA}{}{
    \begin{itemize}
      \item Managed and ran tennis camps for groups of 15 students aged 10 to 14.
      \item Provided one-on-one instruction for adults aged 30 to 50.
      \vspace{5 mm}
    \end{itemize}
  }
\end{document}
